Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-13 paper.tex
saque la palabra setting de la mayor cantidad de lugares posible

A unique (and universal) \textcolor{blue}{set of parameters} appears not
available yet to our knowledge. 
 The reason is that different numerical \textcolor{blue}{set of parameters} can lead to 
the same crowd dynamics. Actually, only a small set of dimensionless 
``numbers'' control the crowd dynamics \cite{dorso_2019}. These are similar to 
those encountered in other active matter systems (P\'eclet number, etc.)  
\cite{marchetti_2014}. We may hypothesize that while the dimensionless 
\textcolor{blue}{parameters} provide some kind of control on the 
collective behavior in 
crowds, only a few numerical settings can attain an ``individualistic'' 
meaning. 
 \\

@@

The fundamental diagram exhibits the flux behavior for either low \textcolor{blue}{density} crowds 
(with \textcolor{blue}{rare} contacts between pedestrians) and highly dense crowds (dominated 
by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{red}{
\sout{In light of our previous hypothesis, we } We} may suspect that the  modeling of the 
``flux slowing down'' within the context of the SFM will require the proper 
setting of the (dimensionless) controlling parameters. We \textcolor{blue}{have already}
examined this working hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
the sliding friction, disregarding the body force. 
We now widen the investigation on the parameter settings to include the one 
associated to the body force. We will  explore 
 the complex interplay between 
the body force and the sliding friction among pedestrians. Recall that the 
interplay dynamics is not directly controlled by the numerical setting, but 
through dimensionless ``numbers'', where the model parameters appear mixed 
between each other. Thus, this step up offers a challenge to the 
``individualistic'' meaning of the parameter's setting. \\

@@

\subsection{\label{parameters}The parameters setting}

The numerical setting of the parameters may affect the dynamics of the 
pedestrians. Some settings, however, yield similar collective dynamics.
We introduce \textcolor{blue}{dimensionless} magnitudes 
and proceed straightforward as indicated in \ref{appendix1}. We realize from 
\ref{appendix1} that only three (\textcolor{blue}{dimensionless}) parameters  are the true 
``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix1}. Recall that 
$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
introduced due to the body force.   \\

@@

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical setting of these parameters may be 
counterbalanced by the right setting of $A$ or $k_t$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\

>>>>

A unique (and universal) \textcolor{blue}{set of parameters} appears not
available yet to our knowledge. 
 The reason is that different numerical \textcolor{blue}{set of parameters} can lead to 
the same crowd dynamics. Actually, only a small set of dimensionless 
``numbers'' control the crowd dynamics \cite{dorso_2019}. These are similar to 
those encountered in other active matter systems (P\'eclet number, etc.)  
\cite{marchetti_2014}. We may hypothesize that while the dimensionless 
\textcolor{blue}{parameters} provide some kind of control on the 
collective behavior in 
crowds, only a few numerical \textcolor{blue}{\sout{settings} set of parameters} can attain an ``individualistic'' 
meaning. 
 \\

@@

The fundamental diagram exhibits the flux behavior for either low \textcolor{blue}{density} crowds 
(with \textcolor{blue}{rare} contacts between pedestrians) and highly dense crowds (dominated 
by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{red}{
\sout{In light of our previous hypothesis, we } We} may suspect that the  modeling of the 
``flux slowing down'' within the context of the SFM will require the proper 
setting of the (dimensionless) controlling parameters. We \textcolor{blue}{have already}
examined this working hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
the sliding friction, disregarding the body force. 
We now widen the investigation on the \textcolor{blue}{\sout{parameter settings} set of parameters} to include the one 
associated to the body force. We will  explore 
 the complex interplay between 
the body force and the sliding friction among pedestrians. Recall that the 
interplay dynamics is not directly controlled by the \textcolor{blue}{\sout{numerical setting} set of parameters}, but 
through dimensionless ``numbers'', where the model parameters appear mixed 
between each other. Thus, this step up offers a challenge to the 
``individualistic'' meaning of the parameter's \textcolor{blue}{\sout{setting} set}. \\

@@

\subsection{\label{parameters} \textcolor{blue}{\sout{The parameters setting} The set of parameters}}

The numerical \textcolor{blue}{\sout{setting} set} of the parameters may affect the dynamics of the 
pedestrians. Some \textcolor{blue}{\sout{settings} sets}, however, yield similar collective dynamics.
We introduce \textcolor{blue}{dimensionless} magnitudes 
and proceed straightforward as indicated in \ref{appendix1}. We realize from 
\ref{appendix1} that only three (\textcolor{blue}{dimensionless}) parameters  are the true 
``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix1}. Recall that 
$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
introduced due to the body force.   \\

@@

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical \textcolor{blue}{\sout{setting} set} of these parameters may be 
counterbalanced by the right \textcolor{blue}{\sout{setting} choise } of $A$ or $k_t$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\
